Parallel global optimization algorithm employing decision trees for launching local methods

### 2025-09-15 2025/MMST_DecisionTree/ParallelDecisionTree.tex
Поправлен текст

	\item Send to process $j$, $1 \leq j \leq n$, the coordinates $y'^{k+1}, \dots, y'^{k+n}$ and notify the process that it needs to perform a single trial.

>>>>

	\item Send to process $j$, $1 \leq j \leq n$, the coordinates of points $y'^{k+1}, \dots, y'^{k+n}$ and notify the process that it needs to perform a single trial.
